Measuring Directionality in Double-Beta Decay and Neutrino Interactions with Kiloton-Scale Scintillation Detectors

### 2013-10-14 Direction_JINST_v1.tex
Direction_JINST_v1.tex has the same content as Direction_v7.tex but is in JINST format. The references have been adjusted to match the JINST journal style. We use JHEP.bst as recommended in the JINST author manual. Direction_JINST_v2.tex has an additional section with three additional plots containing results for 1.4 and 2.1 MeV. Direction_JINST_v3.tex is another iteration of Direction_JINST_v2.tex and Direction_JINST_v4.tex is the version which Andrey, Henry, Matt and Christoph propose for publication. Some more details can be found in README.md --Christoph

%
%%%%%%%%%%%%%%%%%%%%%
% Special Instructions
%%%%%%%%%%%%%%%%%%%%%
%
% Please follow these instructions to use line numbering package (lineno.sty):
%
%   http://fourforces.wordpress.com/2008/04/24/add-line-numbers-using-linenosty-in-revtex-4/
%Cherenkov

@@

\documentclass[aps,prc,twocolumn,groupedaddress,showpacs,amsmath,amssymb,floatfix,superscriptaddress]{revtex4}
\usepackage{multirow}
\usepackage{graphicx,subfigure}
\usepackage{times}
\usepackage{textcomp}
\usepackage{hyperref}
\usepackage{lineno}

\bibliographystyle{apsrev}

\usepackage{color}

@@

%\linenumbers

@@

\bibliographystyle{h-physrev3}

% All university affiliations addresses go here:
\newcommand{\ucla}{\affiliation{University of California Los Angeles, Los Angeles, CA 90095, USA}}
\newcommand{\chicago}{\affiliation{University of Chicago, Chicago, IL 60637, USA}}

%
\author{C.~Aberle}\ucla
\author{A.~Elagin}\chicago
\author{H.~J.~Frisch}\chicago
\author{M.~Wetstein}\chicago
\author{L.~Winslow}\ucla

\date{\today}

\begin{abstract}
Large liquid-scintillator-based detectors have proven to be
exceptionally effective for low energy neutrino measurements due to
their good energy resolution and scalability to large volumes. The
addition of directional information using Cherenkov light and fast
timing would enhance the scientific reach of these detectors,
especially for searches for neutrino-less double-beta decay. In this
paper, we develop a technique for extracting particle direction using
the difference in arrival times for Cherenkov and scintillation light,
and evaluate several detector advances in timing, photodetector
spectral response, and scintillator emission spectra that could be
used to make direction reconstruction a reality in a kiloton-scale
detector.
\end{abstract}

\pacs{23.40.$-$s, 14.60.Pq, 13.15.+g, 29.40.Mc}

\maketitle

@@

\section{Acknowledgments}
The authors thank Andrew Blake at University of Cambridge for his work
authoring the WCSimAnalysis code. The authors thank the neutrino
reconstruction group at Iowa State, particularly Mayly Sanchez, Ioana
Anghel, and Tian Xin, for their continued work in developing the
WCSimAnalaysis algorithms and for their insights and expertise
regarding issues related to Cherenkov reconstruction with
fast-timing. The authors also thank Micheal Smy for his development of
the quadruplet-based vertex-finding method. L. Winslow would like to
thank Janet Conrad for many useful discussion on the topic, and
Katsushi Arisaka for discussions on the possible reach of traditional PMTs
and the characteristics of HPDs. C. Aberle and L. Winslow are
supported by funds from University of California Los Angeles. The work
at the University of Chicago is partially supported by DOE
contract DE-SC0008172 and NSF grant PHY-1066014. Matthew Wetstein gratefully
acknowledges support by the Grainger Foundation.

\bibliography{DirectionBibliography}

>>>>

@@

\documentclass[cits]{JINST}
%%\usepackage{multirow}
\usepackage{times}
%%\usepackage{hyperref}
\usepackage{lineno}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{mathptmx}
\usepackage{mdwlist}
\usepackage{textcomp}
\usepackage{graphicx,subfigure}
\usepackage{fontenc}
%%\usepackage{color}

\author{C.~Aberle$^a$, A.~Elagin$^b$, H.J.~Frisch$^b$, M.~Wetstein$^b$, and L.~Winslow$^a$\setcounter{footnote}{0}\thanks{corresponding author}\\
\llap{$^a$}University of California, Los Angeles, Los Angeles, CA 90095, USA\\
\llap{$^b$}University of Chicago, Chicago, IL 60637, USA\\
  E-mail: \email{lwinslow@physics.ucla.edu}}

\linenumbers

\abstract{Large liquid-scintillator-based detectors have proven to be
exceptionally effective for low energy neutrino measurements due to
their good energy resolution and scalability to large volumes. The
addition of directional information using Cherenkov light and fast
timing would enhance the scientific reach of these detectors,
especially for searches for neutrino-less double-beta decay. In this
paper, we develop a technique for extracting particle direction using
the difference in arrival times for Cherenkov and scintillation light,
and evaluate several detector advances in timing, photodetector
spectral response, and scintillator emission spectra that could be
used to make direction reconstruction a reality in a kiloton-scale
detector.}

\keywords{Scintillators, scintillation and light emission processes (solid, gas and liquid scintillators); Cherenkov detectors; Large detector systems for particle and astroparticle physics; Neutrino detectors; Simulation methods and programs}

@@

@@

@@

\acknowledgments
The authors thank Andrew Blake at University of Cambridge for his work
authoring the WCSimAnalysis code. The authors thank the neutrino
reconstruction group at Iowa State, particularly Mayly Sanchez, Ioana
Anghel, and Tian Xin, for their continued work in developing the
WCSimAnalaysis algorithms and for their insights and expertise
regarding issues related to Cherenkov reconstruction with
fast-timing. The authors also thank Micheal Smy for his development of
the quadruplet-based vertex-finding method. L. Winslow would like to
thank Janet Conrad for many useful discussion on the topic, and
Katsushi Arisaka for discussions on the possible reach of traditional PMTs
and the characteristics of HPDs. C. Aberle and L. Winslow are
supported by funds from University of California Los Angeles. The work
at the University of Chicago is partially supported by DOE
contract DE-SC0008172 and NSF grant PHY-1066014. Matthew Wetstein gratefully
acknowledges support by the Grainger Foundation.

\newpage

\bibliographystyle{JHEP}
\bibliography{DirectionBibliography}
